\documentclass[12pt]{article}

\usepackage[
  a4paper, mag=1000, includefoot,
  left=2cm, right=2cm, top=2cm, bottom=2cm, headsep=1cm, footskip=1cm
]{geometry}
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[english,russian]{babel}
\setlength{\parindent}{0cm}
\parskip 1.5ex
\begin{document}

\section*{Список публикаций}

В. В. Дмитриев, В. В. Завьялов, Д. Е. Змеев, И. В. Косарев, Н. Малдерс.\\
Нелинейный ЯМР  в сверхтекучей В-фазе 3He в аэрогеле.\\
Письма в ЖЭТФ, 76:371--376, 2002.

V. V. Dmitriev, I. V. Kosarev, N. Mulders, V. V. Zavjalov, D. E. Zmeev.\\
Homogeneous spin precession in superfluid 3He confined to aerogel.\\
Physica B: Condensed Matter, vol.329-333, Part 1, Pages 324-326, 2003.\\
Proceedings of the 23rd International Conference on Low Temperature Physics,
LT23, held in Hiroshima, Japan, 20-27 August 2002,

V. V. Dmitriev, I. V. Kosarev, N. Mulders, V. V. Zavjalov, D. E. Zmeev.\\
Measurements of longitudinal and transverse magnetic relaxation in superfluid 3He confined to aerogel.\\
Physica B: Condensed Matter, vol.329-333, Part 1, Pages 322-323,, 2003.\\
Proceedings of the 23rd International Conference on Low Temperatur Physics,
LT23, held in Hiroshima, Japan, 20-27 August 2002,

V. V. Dmitriev, I. V. Kosarev, N. Mulders, V. V. Zavjalov, D. E. Zmeev.\\
Pulsed NMR experiments in superfluid 3He confined to aerogel.\\
Physica B: Condensed Matter, vol.329-333, Part 1, Pages 296-298, 2003.\\
Proceedings of the 23rd International Conference on Low Temperature Physics,
LT23, held in Hiroshima, Japan, 20-27 August 2002,

Vladimir V Dmitriev, Ivan V Kosarev, Norbert Mulders, Vladislav V Zavjalov, Dmitry Ye Zmeev.\\
Experiments on A-like to B phase transitions of 3He confined to aerogel.\\
Physica B: Condensed Matter, 329-333, Part 1(0):320 -- 321, 2003.\\
Proceedings of the 23rd International Conference on Low Temperature Physics,
LT23, held in Hiroshima, Japan, 20-27 August 2002,

А.Н.Выставкин, В.В.Дмитриев, В.В.Завьялов, А.Г.Коваленко, С.А.Ковтонюк, А.А.Чеботарев\\
Исследование сверхпроводникового фазового перехода в двухслойной структуре молибден-медь с эффектом близости\\
Радиотехника и электроника, т.48, N7, 2003.

В. В. Дмитриев, В. В. Завьялов, Д. Е. Змеев, И. В. Косарев, Н. Малдерс.\\
Свeрхтекучие фазы 3Не в аэрогеле.\\
Успехи физических наук, 173(4):452--456, 2003.

В. В. Дмитриев, В. В. Завьялов, Д. Е. Змеев, Н. Малдерс.\\
Измерения леггеттовской частоты в 3He-B в аэрогеле.\\
Письма в ЖЭТФ, 79:612--617, 2004.

V. V. Dmitriev, V. V. Zavjalov, D. Ye. Zmeev, L. V. Levitin.\\
Purification of 3He from a 4He Impurity Using Adsorption.\\
Instruments and Experimental Techniques, 47:567--569, 2004.

V.V. Dmitriev, L.V. Levitin, V.V. Zavjalov, D.Ye. Zmeev.\\
Separation of 3He from 3He-4He Mixture by means of Adsorption.\\
Journal of Low Temperature Physics, 138:877--880, 2005.

V.V. Dmitriev, V.V. Zavjalov, D.Ye. Zmeev.\\
Spatially homogeneous oscillations of homogeneously precessing domain in 3He-B.\\
Journal of Low Temperature Physics, 138:765--770, 2005.

V. V. Dmitriev, N. Mulders, V. V. Zavjalov, D. E. Zmeev.\\
CW NMR Measurements of the Leggett Frequency in 3He-B in Aerogel.\\
AIP Conference Proceedings, 850:229--230, 2006.

V. V. Dmitriev, N. Mulders, V. V. Zavjalov, D. E. Zmeev.\\
NMR Studies of Texture in the B-like  Phase of 3He in Aerogel.\\
AIP Conference Proceedings, 850:225--228, 2006.

V. Dmitriev, D. Krasnikhin, N. Mulders, V. Zavjalov, D. Zmeev.\\
Transverse and longitudinal nuclear magnetic resonance in superfluid 3He in anisotropic aerogel.\\
JETP Letters, 86:594--599, 2008.

Завьялов В.В.\\
Измерение леггеттовской частоты 3He-B в аэрогеле\\
Автореферат диссертации на соискание ученой степени к.ф.-м.н. Москва, 2011

\end{document}
